Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
[Minor]

\heading{Limitations}
Our is implementation is limited in many ways, so as to succeed in proving the key hypothesis---that scaling out shell pipelines can be automated and correct\TODO{with respect to some assumptions}--- despite \sys being a research prototype.

\sys does not adequately handle failures or network partitions in the general sense, which would include re-scheduling passes that were executing on failed replicas.
Prior work on fault-tolerant distributed stream processing~\cite{} can be of significant aid here.

The logic of the planner is quite simplified, attempting only straightforward placement of tasks to nodes (and using a hard-coded, homogeneous node structure).
Prior work on operator placement of distributed dataflow graphs~\cite{} can be used to improve it.

\sys is conservative in the shell subsets that it handles, in order to
not introduce unsafe behaviours. The point of this work was not to be
able to handle a complete distributable subset of the shell, but
rather use significant part of it to demonstrate performance benefits.

Shell is highly dynamic, thus making it impossible to design sound
meaningful analyses to determine distributable regions and maximal
parallelization. In order to address this particularity, \sys could be
tighly integrated with a posix compliant shell
interpreter~\cite{smoosh:20} so that dynamic information can be
acquired selectively to aid the analysis and optimization process.

@@

Another direction is to extend \sys to handle other classes outside \sta and \pur.
These two classes enjoy a certain in quick, one-off pipelines and are the easiest to distribute, but 
it would be interesting to expand to \dfs (with the use of a distributed file-system) and \sid (with the use of transactional protocols).
This direction would naturally introduce considerations about replication, consistency, and failure recovery.

>>>>

\heading{Limitations}
Our implementation is limited in many ways, so as to succeed in proving the key hypothesis---that scaling out shell pipelines can be automated and correct with respect to some assumptions.

\sys does not adequately handle failures or network partitions in the general sense, which would include re-scheduling passes that were executing on failed replicas.
Prior work on fault-tolerant distributed stream processing can be of significant aid here.

The logic of the planner is quite simplified, attempting only straightforward placement of tasks to nodes (and using a hard-coded, homogeneous node structure).
Prior work on operator placement of distributed dataflow graphs can be used to build a more sophisticated planner.

\sys is conservative in the shell subsets that it handles, in order to
avoid introducing unsafe behaviours. The point of this work was not to be
able to handle a complete distributable subset of the shell, but
rather to use significant part of it to demonstrate performance benefits.

% Shell is highly dynamic, thus making it impossible to design sound
% meaningful analyses to determine distributable regions and maximal
% parallelization. In order to address this particularity, \sys could be
% tighly integrated with a posix compliant shell
% interpreter~\cite{smoosh:20} so that dynamic information can be
% acquired selectively to aid the analysis and optimization process.

@@

Another direction is to extend \sys to handle other classes outside \sta and \pur.
These two classes enjoy a certain popularity with quick, one-off pipelines and are the easiest to distribute, but 
it would be interesting to expand to \dfs (with the use of a distributed file-system) and \sid (with the use of transactional protocols).
This direction would naturally introduce considerations about replication, consistency, and failure recovery.
